%---------------------------------------------------------------------------%
%->> Frontmatter
%---------------------------------------------------------------------------%
%-
%-> Titlepage
%-
\maketitle
%-
%-> Examining Committee Membership
%-
\intotoc*{\cleardoublepage}{Examining Committee Membership}% add link to toc
\begin{committee}
    \noindent
    The following served on the Examining Committee for this thesis. The decision of the Examining Committee is by majority vote.

    \begin{center}
        %\footnotesize% fontsize
        \setlength{\tabcolsep}{10pt}% column separation
        \renewcommand{\arraystretch}{3}% row space 
        \begin{tabular}{lc}
            External Examiner & \parbox[t]{10cm}{Dr. Luc Bauwens\\Professor, Mechanical and Manufacturing Engineering\\University of 
Calgary}\\
            Supervisors & \parbox[t]{10cm}{Dr. Fue-Sang Lien\\Professor, Mechanical and Mechatronics Engineering\\University of Waterloo}\\
             & \parbox[t]{10cm}{Dr. Fan Zhang\\Senior Scientist, Advanced Energetics Group\\Defence Research and Development Canada}\\
             & \parbox[t]{10cm}{Dr. Duane Cronin\\Professor, Mechanical and Mechatronics Engineering\\University of Waterloo}\\
            Internal Members & \parbox[t]{10cm}{Dr. Cecile Devaud\\Professor, Mechanical and Mechatronics Engineering\\University of Waterloo}\\
             & \parbox[t]{10cm}{Dr. Jean-Pierre Hickey\\Professor, Mechanical and Mechatronics Engineering\\University of Waterloo}\\
            Internal-External Member & \parbox[t]{10cm}{Dr. Lilia Krivodonova\\Professor, Applied Mathematics\\University of Waterloo}\\
        \end{tabular}
    \end{center}
\end{committee}
%-
%-> Author's declaration
%-
\intotoc*{\cleardoublepage}{Author's Declaration}% add link to toc
\begin{declaration}
    \noindent
    I hereby declare that I am the sole author of this thesis. This is a true copy of the thesis, including any required final revisions, as accepted by my examiners.

    \bigskip

    \noindent
    I understand that my thesis may be made electronically available to the public.
\end{declaration}
%-
%-> Statement of Contributions
%-
%\intotoc*{\cleardoublepage}{Statement of Contributions}% add link to toc
%\begin{contribute}
%\end{contribute}
%-
%-> Permissions
%-
%\intotoc*{\cleardoublepage}{Permissions}% add link to toc
%\begin{permission}
%    \noindent
%\end{permission}
%-
%-> Abstract
%-
\intotoc*{\cleardoublepage}{Abstract}% add link to toc
\begin{abstract}
    This is a short brochure on how to write your thesis by using this \LaTeX{} template. It's easy, efficient and straightforward. What you need to do, no matter you are familiar with \LaTeX{} or not, is to have a try.
\end{abstract}
%-
%-> Acknowledgements
%-
\intotoc*{\cleardoublepage}{Acknowledgements}% add link to toc
\begin{acknowledgements}

    I owe my deepest gratitude and appreciation to my doctoral advisors: Dr. Fue-Sang Lien, Dr. Fan Zhang, and Dr. Duane Cronin. Dr. Fue-Sang Lien has always been supportive, approachable, and helpful throughout my doctoral study. His encouragement and understanding helped me go through the difficulties and created the space for me to develop research ideas. Working with Dr. Fan Zhang has been the most amazing experience in my life. I have always been fascinated by his insights on physics and the ability to instantly and accurately identify the key problems based on a set of fragmented information. His keen and open-minded guidance inspired my interests in the field of my doctoral study, shaped my critical thinking, and challenged me to be a higher level thinker. It was an enlightening and enriching experience to collaborate with Dr. Duane Cronin. Whenever I needed advice, he was ready and patient to help. He was always kind to teach me and willing to share his experience and vision on how to be a professional, rigorous, and persuasive researcher. The moments I interacted with and the knowledge I learned from my outstanding advisors will be remembered by me throughout the rest of my life.

    I am grateful to Natural Sciences and Engineering Research Council of Canada (NSERC), Defence Research and Development Canada (DRDC), and Waterloo CFD Engineering Consulting Inc (WATCFD) for the financial support of this research project. This work was made possible by the facilities of the Shared Hierarchical Academic Research Computing Network (SHARCNET: www.sharcnet.ca) and Compute/Calcul Canada.

    I would like to thank the official members of my examining committee for their efforts in reviewing my thesis and providing helpful suggestions. In addition, I want to express my gratitude to Dr. Jean-Pierre Hickey for his kind help with my teaching practice, to Dr. Cecile Devaud for her helpful comments on my comprehensive examination report, to Dr. Lilia Krivodonova for her thoughtful teaching on numerical solutions of partial differential equations, and to Dr. Luc Bauwens for taking his time to come and attend my examination in person. I also want to thank my colleagues in the Energy Research Center for their support and discussions and the faculty and staff in the Mechanical and Mechatronics Engineering department for their assistance and help throughout my doctoral study. Finally, I am indebted to my family for their continuous support and understanding with my pursuit of scientific research.

\end{acknowledgements}
%-
%-> Dedication
%-
%\intotoc*{\cleardoublepage}{Dedication}% add link to toc
%\begin{dedication}
%    Dedication (included if necessary)
%\end{dedication}
%---------------------------------------------------------------------------%
